---
title: "Exercise 1"
date: "2024-09-26"
bibliography: biblio.bib
# 4. Highlight the code using monochrome style.
output:
  html_document:
    highlight: monochrome
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("knitr")
library (knitr)
```

## Lecture 2: R Markdown

2\. Create a new header of type 2 (i.e., \## Header Text).

## Header Text Type 2

3.  Perform a linear regression with ”Sepal Length” as the response and ”Sepal Width” as the explanatory variable from the iris dataset. Save the result.

```{r}

model <- lm(iris$Sepal.Length ~ iris$Sepal.Width, data = iris)


```

5.  Print the summary of the linear regression.

```{r}
summary(model)
```

6.  Include the QQ plot from the linear regression and change the points to filled dots.

```{r}
qqnorm(fitted(model), main = "QQ Plot of Fitted Values", pch=19)

```

7.  Print the head of the iris dataset using kable.

```{r}
kable(head(iris))
```

8.  Remove the period from the column labels.

```{r}
kable(iris, col.names = gsub("[.]", " ", names(iris)))
```

### More advanced manipulations:

1.  Install kableExtra. Perform the examples shown in the slides with the iris dataset.

```{r}
install.packages("kableExtra")
library(kableExtra)
iris[1:3, 1:3] %>%
  kbl() %>%
  kable_paper(full_width = F) %>%  
  column_spec(3, color = spec_color(iris$Sepal.Width[1:3]),
              link = "https://haozhu233.github.io/kableExtra/") %>%
  column_spec(3, color = "white",
              background = spec_color(iris$Petal.Length[1:3], end = 0.7),
              popover = paste("am:", iris$Petal.Width[1:3]))
```

2.  Using Mathpix, reproduce equation (6.1) from the paper available at <https://arxiv.org/abs/math/0303109>. $$
    2 \sqrt{t_0 - t_\gamma} \int_{t_\gamma}^{t_0} \sqrt{t_0 - t} \left( R(\gamma(t), t) + |\dot{\gamma}(t)|^2 \right) dt \geq C(A) r_0^2
    $$

3.  Add the reference for the paper and cite it in the RMarkdown file. (@perelman2003ricci)

4.  Recreate your RMarkdown file as a Quarto document.

## Lecture 3: GitHub

1.  Create a GitHub repository for the RMarkdown file (.Rmd) you created in the previous exercise.

    <https://github.com/MariGandarillas98/Exercise-1>

2.  Edit the README.md file and push the .Rmd to the repository.

3.  Collaborate with another person (Person A and Person B):

    -   Ensure the repository is up-to-date. Person B modifies the .Rmd and pushes the changes, then Person A pulls the changes.
    -   Ensure the repository is up-to-date. Person A modifies the 1st section of the .Rmd, while Person B modifies the 2nd section (no conflict). No push or pull in between. Person A commits and pushes, then Person B attempts to push and solve any merge conflicts.
    -   Handle conflicts when both Person A and Person B modify the same section of the .Rmd.

## References
